%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[colorlinks=true,
            linkcolor=blue,
            urlcolor=blue,
            citecolor=blue,
            anchorcolor=blue]{hyperref}

\newcommand{\MYhref}[3][blue]{\href{#2}{\color{#1}{#3}}}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Sangbum Daniel Choi} & Email : \href{mailto:danielsejong55@gmail.com}{danielsejong55@gmail.com}\\
  \href{https://www.linkedin.com/in/daniel-choi-86648216b/}{linkedin.com/in/daniel-choi-86648216b} & Mobile : +82-010-5913-2857 \\
  \href{https://github.com/SangbumChoi}{github.com/SangbumChoi} &
  {Updated: 2026/05/30}\\
\end{tabular*}

%-----------SUMMARY-----------------
\section{Summary}
AI systems engineer with 6+ years of experience building multimodal vision models, production ML training/serving infrastructure, and open-source model integrations in Hugging Face Transformers. Experienced in inference optimization with TensorRT/Triton, large-scale model deployment, model conversion, efficient training, and performance-oriented ML systems.

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Toss Bank}{Seoul, South Korea}
      {Data Scientist}{Jan 2026 - Present}
      \resumeItemListStart
        \resumeItem{On-premise AI Agent System}
          {Building an on-premise opencode agent system for secure internal AI-assisted development workflows in a banking environment.}
        \resumeItem{AI-based Authentication}
          {Developing AI-based authentication models and pipelines for face verification and ID card verification.}
        \resumeItem{Document Information Extraction}
          {Developing document AI systems to extract structured information from banking documents and identity verification flows.}
      \resumeItemListEnd

    \resumeSubheading
      {SuperbAI}{Seoul, South Korea}
      {Machine Learning Engineer}{Sep 2021 - Jan 2026}
      \resumeItemListStart
        \resumeItem{[Lead] Vision Foundation Model}
          {Spearheaded a multi-modal vision foundation model that accepts text and semantic prompts for object detection and segmentation; led two ML engineers through planning, dataset construction, training, API deployment, and AWS Marketplace release.}
        \resumeItem{Dataset and Evaluation}
          {Prepared a 1.1M-image in-house dataset and used automated model-assisted verification to improve labeling efficiency; won 2nd place in IOD and 4th place in FSOD at CVPR 2025 challenges.}
        \resumeItem{[Lead] ML Training \& Serving Platform}
          {Designed AWS Batch based training infrastructure and optimized production inference with TensorRT and Triton Inference Server, improving throughput by 5x over pure PyTorch serving.}
        \resumeItem{Scale}
          {Generated 1,100+ machine learning models and 60+ customer endpoints in one year across customer tenants.}
        \resumeItem{Efficient Training}
          {Reduced GPU memory usage by 65.6\% and training time by 44.3\% using parameter- and memory-efficient methods for large models while preserving model performance.}
        \resumeItem{Vision Language Model}
          {Developed a flexible pipeline for applying LoRA, Adapter, and LST methods to reduce computational cost and participated in the CVPRW 2023 NICE challenge.}
        \resumeItem{Web ML}
          {Developed browser, hybrid, and cloud-based interactive segmentation tools using RepViT-SAM, FocalClick, SAM, and SAM2; increased segmentation labeling speed by 25x and built video tracking with fine-tuned personalized SAM.}
        \resumeItem{Transfer Learning}
          {Developed pretraining and parameter-efficient transfer learning algorithms using DETR architectures and CBNetV2; built multi-domain datasets such as night and aerial imagery with box and polygon annotations.}
        \resumeItem{Uncertainty Estimation}
          {Implemented Monte Carlo dropout for keypoint and segmentation models, reducing human inspection effort to 30\% by ranking predictions with top uncertainty scores.}
      \resumeItemListEnd

    \resumeSubheading
      {Kakao Enterprise}{Pangyo, South Korea}
      {Machine Learning Engineer Intern}{Feb 2021 - Aug 2021}
      \resumeItemListStart
        \resumeItem{AutoML}
          {Fixed the scaling issue of AutoGluon's NeuralNetFastAI algorithm and developed a Flask-based training/inference AutoML framework with a simple front-end.}
      \resumeItemListEnd

    \resumeSubheading
      {Team ISLAND}{Seoul, South Korea}
      {Chief Technology Officer}{Mar 2019 - Oct 2020}
      \resumeItemListStart
        \resumeItem{Startup}
          {Created an MZ video production platform based on scribble effects; led development, investor relations, and product management with a five-person team across Android, Unity, and deep learning.}
        \resumeItem{Fundraising}
          {Prepared investor pitch materials and helped raise approximately \$290K through government subsidies and seed funding.}
        \resumeItem{Mobile ML}
          {Developed a lightweight 3D human pose estimation model for mobile devices and converted PyTorch models to TensorFlow Lite.}
      \resumeItemListEnd

    \resumeSubheading
      {Seerslab Inc.}{Seoul, South Korea}
      {Software Engineer Intern}{Jul 2018 - Aug 2018}
      \resumeItemListStart
        \resumeItem{Annotation Tool}
          {Developed a facial landmark annotation tool using D-lib, Python, and PyQt.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------OPEN SOURCE-----------------
\section{Open Source}
  \resumeSubHeadingListStart
    \resumeSubItem{\MYhref{https://github.com/huggingface/transformers/pulls?q=is\%3Apr+SangbumChoi}{Hugging Face Transformers}}
      {Contributed 40+ pull requests across multimodal, vision, and object-detection models, including SAM2, Molmo2, RT-DETR, ViTPose, DINOv3 utilities, zero-shot examples, and training/inference fixes.}
    \resumeSubItem{\MYhref{https://github.com/huggingface/transformers/pull/32317}{Hugging Face Transformers - Segment Anything 2}}
      {Led the integration of SAM2 into Transformers across model architecture, image/video processing, conversion scripts, documentation, and integration tests. The PR was merged on 2025-08-13 after a long community review cycle and is credited in the official \MYhref{https://huggingface.co/docs/transformers/model_doc/sam2}{SAM2 documentation}.}
    \resumeSubItem{\MYhref{https://github.com/huggingface/transformers/pull/43451}{Hugging Face Transformers - Molmo2}}
      {Opened Molmo2 support for Transformers, including model integration work for a multimodal VLM family, and published \MYhref{https://huggingface.co/danelcsb/Molmo2-4B}{danelcsb/Molmo2-4B} on the Hugging Face Hub.}
    \resumeSubItem{\MYhref{https://github.com/huggingface/transformers/pull/29077}{RT-DETR}}
      {Implemented RT-DETR support in Transformers.}
    \resumeSubItem{\MYhref{https://github.com/huggingface/transformers/pull/30530}{ViTPose}}
      {Implemented ViTPose support in Transformers.}
    \resumeSubItem{Training and Distributed Fixes}
      {Fixed DETA auxiliary training loss issue and improved gathering behavior in multi-GPU training pipelines; additional contributions are available in \MYhref{https://github.com/huggingface/transformers/pulls?q=sangbumchoi}{Transformers pull requests}.}
  \resumeSubHeadingListEnd

%-----------PAPERS----------------
\section{\MYhref{https://scholar.google.co.kr/citations?user=4klHsscAAAAJ&hl=ko}{Papers}}
  \resumeSubHeadingListStart
    \resumeSubItem{ZERO: Multi-modal Prompt-based Visual Grounding}
      {arXiv - Jul 6, 2025}
    \resumeSubItem{MobileHumanPose: Toward real-time 3D human pose estimation in mobile devices}
      {IEEE/CVF CVPR Workshop - Jun 19, 2021}
  \resumeSubHeadingListEnd

%-----------TALKS----------------
\section{Presentations}
  \resumeSubHeadingListStart
    \resumeSubItem{Building Vision Foundation Model in Startup}
      {Superb AI First Online Seminar - Oct 29, 2025}
    \resumeSubItem{\MYhref{https://events.ringcentral.com/events/mlops-world-machine-learning-in-production-bay-area/registration}{Automation in AutoLabeling}}
      {MLOps World: Machine Learning in Production Bay Area - Jun 19, 2022}
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Stable Diffusion}
      {Generated personalized portraits and customized styles by fine-tuning diffusion weights with LoRA.}
    \resumeSubItem{\MYhref{https://github.com/SangbumChoi/SuperbMobile}{iOS Inspection App}}
      {Built an in-house iOS data inspection function for project managers and distributed it through TestFlight.}
    \resumeSubItem{Binaural Sound}
      {Generated a human evaluation metric for binaural sound generation.}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {KAIST (Korea Advanced Institute of Science and Technology)}{Daejeon, South Korea}
      {Professional Master in Electrical Engineering; GPA: 3.55/4.3}{Feb. 2020 -- Aug. 2021}
    \resumeSubheading
      {POSTECH (Pohang University of Science and Technology)}{Pohang, South Korea}
      {Bachelor in Electrical Engineering; GPA: 3.4/4.3}{Mar. 2015 -- Feb. 2020}
    \resumeSubheading
      {UIUC (University of Illinois Urbana-Champaign)}{Illinois, United States}
      {Exchange Student; GPA: 3.6/4.0}{Jan. 2018 -- Dec. 2018}
    \resumeSubheading
      {Sejong Science High School}{Seoul, South Korea}
      {One year early graduation}{Mar. 2013 -- Feb. 2015}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{AI Systems}{: Python, PyTorch, Transformers, TensorRT, Triton, AWS}
     \hfill
     \textbf{Experienced}{: TensorFlow, model conversion, Swift, LangChain, Langfuse}
   }
 \resumeSubHeadingListEnd

\end{document}
