%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[colorlinks=true,
            linkcolor=blue,
            urlcolor=blue,
            citecolor=blue,
            anchorcolor=blue]{hyperref}

\newcommand{\MYhref}[3][blue]{\href{#2}{\color{#1}{#3}}}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Sangbum Daniel Choi} & Email : \href{mailto:danielsejong55@gmail.com}{danielsejong55@gmail.com}\\
  \href{https://www.linkedin.com/in/daniel-choi-86648216b/}{linkedin.com/in/daniel-choi-86648216b} & Mobile : +82-010-5913-2857 \\
  \href{https://github.com/SangbumChoi}{github.com/SangbumChoi} &
  {Updated: 2026/07/17}\\
\end{tabular*}

%-----------SUMMARY-----------------
\section{Summary}
Applied scientist and research engineer with 6+ years of experience taking multimodal models from data design and pre/post-training through rigorous evaluation and production deployment. Led end-to-end VLM and visual-grounding projects, built scalable PyTorch training/serving systems, and contributed 40+ pull requests to Hugging Face Transformers.

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Toss Bank}{Seoul, South Korea}
      {Data Scientist}{Jan 2026 - Present}
      \resumeItemListStart
        \resumeItem{On-premise AI Agent System}
          {Building an on-premise agent system with internally deployed LLMs for secure AI-assisted development workflows.}
        \resumeItem{AI Authentication}
          {Developing AI-based authentication systems for face and ID card verification.}
        \resumeItem{[Lead] End-to-End Document AI}
          {Led the full research and production pipeline for an approximately 1B-parameter vision-language model, spanning multi-page classification, orientation, layout detection, OCR/table understanding, and LLM-based key-value extraction; post-trained the model, designed stage-level diagnostics, and reached 61\% exact-match accuracy for automation-ready outputs.}
      \resumeItemListEnd

    \resumeSubheading
      {SuperbAI}{Seoul, South Korea}
      {Machine Learning Engineer}{Sep 2021 - Jan 2026}
      \resumeItemListStart
        \resumeItem{[Lead] Multimodal Foundation Model}
          {Led multimodal pre-training and staged text/image alignment for a visual-grounding model; designed and curated 1.1M images with captions, boxes, and masks, then drove benchmark evaluation, API deployment, and AWS Marketplace release.}
        \resumeItem{CVPR 2025 Competitions}
          {Won 2nd place in IOD and 4th place in FSOD challenges, validating the model on open evaluation benchmarks.}
        \resumeItem{[Lead] ML Training \& Serving Platform}
          {Built reusable distributed multi-GPU training, evaluation, and deployment infrastructure with PyTorch and AWS Batch; optimized production serving with TensorRT/Triton, improving throughput by 5x and delivering 1,100+ models and 60+ customer endpoints in one year.}
        \resumeItem{Post-training and Efficiency}
          {Applied LoRA, Adapter, and LST methods and memory-efficient training, reducing GPU memory by 65.6\% and training time by 44.3\% while preserving model performance.}
        \resumeItem{Interactive Segmentation}
          {Built browser, hybrid, and cloud-based segmentation tools using RepViT-SAM, FocalClick, SAM, and SAM2, increasing segmentation labeling speed by 25x.}
      \resumeItemListEnd

    \resumeSubheading
      {Kakao Enterprise}{Pangyo, South Korea}
      {Machine Learning Engineer Intern}{Feb 2021 - Aug 2021}
      \resumeItemListStart
        \resumeItem{AutoML}
          {Fixed AutoGluon NeuralNetFastAI scaling issue and developed a Flask-based training/inference AutoML framework with a simple front-end.}
      \resumeItemListEnd

    \resumeSubheading
      {Team ISLAND}{Seoul, South Korea}
      {Chief Technology Officer}{Mar 2019 - Oct 2020}
      \resumeItemListStart
        \resumeItem{Startup}
          {Raised approximately \$290K through government subsidies and seed funding; managed five developers across Android, Unity, and deep learning workstreams.}
        \resumeItem{Mobile ML}
          {Built \MYhref{https://www.venturesquare.net/821623}{ZZAZZ}, a mobile video editor using detection/segmentation, 3D mapping, and tracking; deployed lightweight vision models through TensorFlow Lite.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------OPEN SOURCE-----------------
\section{Open Source}
  \resumeSubHeadingListStart
    \resumeSubItem{\MYhref{https://github.com/huggingface/transformers/pulls?q=is\%3Apr+SangbumChoi}{Hugging Face Transformers}}
      {Contributed 40+ pull requests to a large production codebase across multimodal and vision models, independently shipping model architectures, processors, conversion scripts, distributed training fixes, tests, and documentation.}
    \resumeSubItem{\MYhref{https://github.com/huggingface/transformers/pull/32317}{Hugging Face Transformers - SAM2}}
      {Led the addition of Segment Anything 2 support to Transformers, including model integration, image/video processors, conversion flow, documentation, and tests; credited in the official \MYhref{https://huggingface.co/docs/transformers/model_doc/sam2}{SAM2 docs}.}
    \resumeSubItem{\MYhref{https://github.com/huggingface/transformers/pull/43451}{Hugging Face Transformers - Molmo2}}
      {Opened Molmo2 support for Transformers and published \MYhref{https://huggingface.co/danelcsb/Molmo2-4B}{danelcsb/Molmo2-4B} on the Hugging Face Hub.}
  \resumeSubHeadingListEnd

%-----------PAPERS----------------
\section{\MYhref{https://scholar.google.co.kr/citations?user=4klHsscAAAAJ&hl=ko}{Papers}}
  \resumeSubHeadingListStart
    \resumeSubItem{ZERO: Multi-modal Prompt-based Visual Grounding}
      {arXiv - Jul 6, 2025}
    \resumeSubItem{MobileHumanPose: Toward real-time 3D human pose estimation in mobile devices}
      {IEEE/CVF CVPR Workshop - Jun 19, 2021}
    \resumeSubItem{Improved DOA estimation of MUSIC algorithm based on irregular microphone array}
      {UIUC Research - Dec 20, 2018}
    \resumeSubItem{On Joint Transfer of Energy and Information: A Markov Decision Problem Formulation}
      {Research paper - Dec 13, 2018}
    \resumeSubItem{Terahertz Signal Analysis in Tissue of Gastroesophageal Reflux Disease}
      {Sejong Science High School - Dec 31, 2013}
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {KAIST (Korea Advanced Institute of Science and Technology)}{Daejeon, South Korea}
      {Professional Master in Electrical Engineering; GPA: 3.55/4.3}{Feb. 2020 -- Aug. 2021}
    \resumeSubheading
      {POSTECH (Pohang University of Science and Technology)}{Pohang, South Korea}
      {Bachelor in Electrical Engineering; GPA: 3.4/4.3}{Mar. 2015 -- Feb. 2020}
    \resumeSubheading
      {UIUC (University of Illinois Urbana-Champaign)}{Illinois, United States}
      {Exchange Student; GPA: 3.6/4.0}{Jan. 2018 -- Dec. 2018}
  \resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Research}{: Python, PyTorch, Transformers, multimodal pre/post-training, LoRA, contrastive alignment, evaluation}
     \hfill
     \textbf{Systems}{: Linux, AWS Batch, multi-GPU training, MLflow, TensorRT, Triton, ONNX, TensorFlow Lite, Git}
     \\
     \textbf{Agents}{: LangChain, Langfuse, Claude Code, Codex, opencode}
     \hfill
     \textbf{Languages}{: Korean (native), English (professional)}
   }
 \resumeSubHeadingListEnd

\end{document}
